Merging merges, more or less

### 2015-03-26 2015mergingmerges/section/02-Machines.tex
start on merging inference rules
working on invariants

To begin, we annotate the initial state with an empty set of information: at the start of the machine, we have no read values available, nor is it known (or likely!) that any channels are finished.
Then, for each output transition, we annotate the output state according to the current state type and the transition label: @Pull n@ adds a @Value n@ or @Finished n@ to its @Some n@ and @None@ transitions.
If the output state has already been annotated, we check that the two annotations are the same, modulo values produced by @Out@.
The reason that annotations may be different in the values produced by @Out@ is that the @Out@ values are not explicitly released, and may be referred to by other functions, for example after fusing two combinators together.

>>>>

To begin, we annotate the initial state with an empty set of information: at the start of the machine, we have no read values available, nor is it known (or likely!) that any channels are finished.
Then, for each output transition, we annotate the output state according to the current state type and the transition label: @Pull n@ adds a @Value n@ or @Finished n@ to its @Some n@ and @None@ transitions.
If the output state has already been annotated, we check that the two annotations are the same, modulo values produced by @Out@.
The reason that annotations may be different in the values produced by @Out@ is that the @Out@ values are not explicitly released, and may be referred to by other functions, for example after fusing two combinators together.
See figure~\ref{fig:invariants}.

$$ \CheckOut{\Gamma}{s}{a} $$
Under environment $\Gamma$ and machine $m$, the state $s$ has available information $a$.

$$ \CheckOutTrans{l}{a} $$
Under environment $\Gamma$ and machine $m$, the transition from state $s$ to $t$ under label $l$ has available information $a$.

$$ \CheckStateType{s}{T} $$
In machine $m$, state $s$ has state type $T$.

$$ \Trans{s}{l}{t} \quad \TransU{s}{t}$$
In machine $m$, there is a transition from $s$ to $t$, optionally labelled $l$.
